A Horrocks-type theorem for even orthogonal $K_2$

### 2020-06-19 horrocks.tex
Move bibliography to the end of the paper

%
%    Documenta-LaTeX.sty (2e)
%
%    Version 0.52
%
%    Copyright (C) 1996-2017 Ulf Rehmann
%    rehmann@math.uni-bielefeld.de
%
% ------------------------------ PROLOGUE -----------------------------
%
% This prologue is to be prepended to your LaTeX file in order to
% give it the layout required by Documenta Mathematica.
% Please edit the \documentclass line below, add \usepackage lines
% according to your needs and
% go to the line starting with \Title below, fill in title,
% authors' names and so on and follow the further instructions there.
% 
% Choose one of the commands \documentclass[]{} or \documentstyle[]{}
% depending on the version of LaTeX you use:
%
%
% If you use LaTeX 2e use the following line (or similar):
\documentclass[10pt,a4paper,twoside]{article}
%%\usepackage{hyperref}
% Append here commands \usepackage{...} if you want.
%
% If you use LaTeX 2.09 or earlier use the following line (or similar):
%\documentstyle[10pt,twoside]{article}
%
% Please go to the line starting with \Title below, fill in title,
% authors' names and so on and follow the further instructions there.
%
% The final values of the following 4 uncommented lines will be filled in
% by Doc. Math. after the manuscript has been accepted for publication.
%
\def\YEAR{\year}\newcount\VOL\VOL=\YEAR\advance\VOL by-1995
\def\firstpage{1}\def\lastpage{1000}
\def\received{}\def\revised{}
\def\communicated{}
%

@@

%
%-----------------headlines-----------------------------------
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[breaklinks=false,unicode]{hyperref}
\usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{filecontents}

@@

\def\LOCAL{\horrocks.files}
\begin{filecontents}{horrocks.bib}
@Article{Abe83,
    Title = {Whitehead groups of {C}hevalley groups over polynomial rings},
    Author = {Abe, Eiichi},
    Journal = {Comm. Alg.},
    Year = {1983},
    Number = {12},
    Pages = {1271-1307},
    Volume = {11},
    Doi = {10.1080/00927878308822906} }

@article{La18,
  title={A local-global principle for symplectic $K_2$},
  author={Lavrenov, Andrei},
  year={2018},
  journal={Doc. Math.},
  volume={23},
  pages={653--675},
  doi={10.25537/dm.2018v23.653-675}}
\end{filecontents}

@@

\long\def\MSC#1\EndMSC{\def\arg{#1}\ifx\arg\empty\relax\else
     {\par\narrower\noindent%
     2010 Mathematics Subject Classification: #1\par}\fi}

@@

\begin{document}
%%%%% ------------- fill in your data below this line  -------------------
%%%%%    The following lines \Title ... \EndAddress must ALL be present
%%%%%    and in the given order.
\Title
A Horrocks-type theorem for even orthogonal $\mathrm{K}_2$
\ShortTitle 
A Horrocks-type theorem for $\mathrm{KO}_2$ 
\SubTitle   
%%%%%    A possible subtitle goes here.
\Author 
Andrei Lavrenov and Sergey Sinchuk
\ShortAuthor 
\EndTitle
\Abstract 
We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups. The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, positive solution of which currently is only known in the linear case.
\EndAbstract
\MSC 
19C20
\EndMSC
\KEY 
Steinberg group, $\mathrm{K}_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing.
\EndKEY
%%%%%    All 4 \Address lines below must be present. To center the last
%%%%%    entry, no empty lines must be between the following \Address
%%%%%    and \EndAddress lines.
\Address
Andrei Lavrenov
avlavrenov@gmail.com
\Address
Sergey Sinchuk
sinchukss@gmail.com
\Address
Chebyshev laboratory, 
St. Petersburg State University, 
14th. Line V.O. 29b
199178, St. Petersburg, Russia
\Address
\EndAddress
%%
%%       Make sure the last tex command in your manuscript
%%       before the first \end{document} is the command  \Addresses
%%
%%---------------------Here the prologue ends---------------------------------
%%--------------------Here the manuscript starts------------------------------

@@

\printbibliography
\Addresses
\end{document}

>>>>

%
%    Documenta-LaTeX.sty (2e)
%
%    Version 0.52
%
%    Copyright (C) 1996-2017 Ulf Rehmann
%    rehmann@math.uni-bielefeld.de
%
% ------------------------------ PROLOGUE -----------------------------
%
% This prologue is to be prepended to your LaTeX file in order to
% give it the layout required by Documenta Mathematica.
% Please edit the \documentclass line below, add \usepackage lines
% according to your needs and
% go to the line starting with \Title below, fill in title,
% authors' names and so on and follow the further instructions there.
% 
% Choose one of the commands \documentclass[]{} or \documentstyle[]{}
% depending on the version of LaTeX you use:
%
%
% If you use LaTeX 2e use the following line (or similar):
\documentclass[10pt,a4paper,twoside]{article}
%%\usepackage{hyperref}

% Append here commands \usepackage{...} if you want.
%
% If you use LaTeX 2.09 or earlier use the following line (or similar):
%\documentstyle[10pt,twoside]{article}
%
% Please go to the line starting with \Title below, fill in title,
% authors' names and so on and follow the further instructions there.
%
% The final values of the following 4 uncommented lines will be filled in
% by Doc. Math. after the manuscript has been accepted for publication.
%
\def\YEAR{2020}\newcount\VOL\VOL=\YEAR\advance\VOL by-1995
\def\firstpage{1}\def\lastpage{1000}
\def\received{October 2, 2019}\def\revised{June 11, 2020}
\def\communicated{Max Karoubi}
%

@@

%
%-----------------headlines-----------------------------------
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[breaklinks=false,unicode]{hyperref}
\definecolor{DarkPurple}{rgb}{0.40,0.0,0.20}
\hypersetup{colorlinks=true,citecolor=NavyBlue,linkcolor=DarkPurple,urlcolor=NavyBlue}
\usepackage{color} 
%\usepackage[breaklinks=false,unicode]{hyperref}
\usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{filecontents}

@@

\def\LOCAL{\horrocks.files}

@@

\long\def\MSC#1\EndMSC{\def\arg{#1}\ifx\arg\empty\relax\else
     {\par\narrower\noindent%
     2020 Mathematics Subject Classification: #1\par}\fi}

@@

\begin{document}
%%%%% ------------- fill in your data below this line  -------------------
%%%%%    The following lines \Title ... \EndAddress must ALL be present
%%%%%    and in the given order.
\Title
A Horrocks-Type Theorem for Even Orthogonal $\mathrm{K}_2$
\ShortTitle 
A Horrocks-Type Theorem for $\mathrm{KO}_2$ 
\SubTitle   
%%%%%    A possible subtitle goes here.
\Author 
Andrei Lavrenov and Sergey Sinchuk
\ShortAuthor 
A. Lavrenov, S. Sinchuk
\EndTitle
\Abstract 
We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups. The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, positive solution of which currently is only known in the linear case.
\EndAbstract
\MSC 
19C20
\EndMSC
\KEY 
Steinberg group, $\mathrm{K}_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing
\EndKEY
%%%%%    All 4 \Address lines below must be present. To center the last
%%%%%    entry, no empty lines must be between the following \Address
%%%%%    and \EndAddress lines.
\Address
Andrei Lavrenov
Chebyshev Laboratory 
St. Petersburg State University 
14th. Line V.O. 29b
199178, St. Petersburg
Russia
avlavrenov@gmail.com
\Address
Sergey Sinchuk
Chebyshev Laboratory 
St. Petersburg State University 
14th. Line V.O. 29b
199178, St. Petersburg
Russia
sinchukss@gmail.com
\Address
\Address
\EndAddress
%%
%%       Make sure the last tex command in your manuscript
%%       before the first \end{document} is the command  \Addresses
%%
%%---------------------Here the prologue ends---------------------------------
%%--------------------Here the manuscript starts------------------------------

@@

\printbibliography
\Addresses
\begin{filecontents}{horrocks.bib}
@Article{Abe83,
    Title = {Whitehead groups of {C}hevalley groups over polynomial rings},
    Author = {Abe, Eiichi},
    Journal = {Comm. Alg.},
    Year = {1983},
    Number = {12},
    Pages = {1271-1307},
    Volume = {11},
    Doi = {10.1080/00927878308822906} }

@article{La18,
  title={A local-global principle for symplectic $K_2$},
  author={Lavrenov, Andrei},
  year={2018},
  journal={Doc. Math.},
  volume={23},
  pages={653--675},
  doi={10.25537/dm.2018v23.653-675}}
\end{filecontents}
\end{document}
